The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-11-21 paper/ms.tex
remove comments
author list

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Timothy R. Bedding,$^{8,5}$
Allyson Bieryla,$^{9}$
David W. Latham,$^{9}$,
Conny Aerts,$^{10,11,12}$\newauthor
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Dominic M. Bowman,$^{10}$
Ashley Chontos,$^{13}$\newauthor
Gilbert A. Esquerdo,$^{9}$
Daniel Huber,$^{13,14,8}$
Paula Jofr\'{e},$^{15}$
Simon Murphy,$^{8,5}$\newauthor
Timothy van Reeth,$^{8,5}$
Victor Silva Aguirre,$^{5}$
Amalie Stokholm,$^{5}$
Jie Yu,$^{8,5}$ \newauthor
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{9}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{10}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{11}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{12}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{14}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{15}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

%\begin{figure*}
%\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}
%
%\caption{\label{alphael}
%The [Mg/Fe], [Si/Fe], [Ca/Fe], and [Ti/Fe], [Al/Fe], [Na/Fe] abundance ratios as a function of iron on the top and bottom rows, respectively for our stars (black cirlces). We also illustrate a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014} and \citet[open orange triangles,][]{Adibekyan2012}. } 
%\end{figure*}

@@

%place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from. May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys

@@

%\appendix
%\section{Full Chemical Analysis}
%The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. In Fig.~\ref{fig:alphael}, we show the chemical abundance pattern of [Mg/Fe] as a function of metallicity of our sample (in black) as well two representative Galactic disk samples. It is clear from that figure that our sample is largely drawn from the Galactic disk from a chemical perspective. Below we provide further evidence of this with other elements across three families. 
%
%In Fig.~\ref{fig:alphael_appendix}, we display the abundances of the remaining $\alpha$-elements (including Ti, Si, Ca) as well as the odd-Z elements (Al, Cu, Sc, V). In Fig.~\ref{fig:Fepeak_appendix} we show the Fe-peak elements (Fe, Ni, Zn, Co, Cr, Mn) and in Fig.~\ref{fig:ncapture_appendix}  we show the Neutron-Capture elements. In each diagram we plot the [X/Fe] abundance ration as a function of metallicity. For reference, the typical chemical abundances pattern in the Galactic disk is shown for each element and are taken from Bensby2014, Adibekyan2012,

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Allyson Bieryla,$^{8}$
David W. Latham,$^{8}$,
Conny Aerts,$^{9,10,11}$
Suzanne Aigrain,$^{3}$ \newauthor
Victoria Antoci,$^{5}$
Timothy R. Bedding,$^{12,5}$
Dominic M. Bowman,$^{10}$
Ashley Chontos,$^{13}$\newauthor
Gilbert A. Esquerdo,$^{8}$
Daniel Huber,$^{13,14,8}$
Paula Jofr\'{e},$^{15}$
Simon Murphy,$^{12,5}$\newauthor
Timothy van Reeth,$^{12,5}$
Victor Silva Aguirre,$^{5}$
Amalie Stokholm,$^{5}$
Jie Yu$^{12,5}$ 
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{11}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
$^{12}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{14}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{15}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

@@

@@

@@
